\chapter{Articles}
\section{Review}
%
%
%----------------------------------------------------------------//
\subsection[Ge, Wei, 2019]{Ge, Wei, 2019, \cite{ge2019multiscale}}
\textit{Multiscale structures in particle--fluid systems: Characterization, modeling, and simulation.}

This is a very general paper that focused on the mesoscale structure in the particle-fluid system, or the clusters in the fluidized bed. 
The paper discussed not only the experimental researches but also the modeling studies. 
%
%
%----------------------------------------------------------------//
\subsection[Zhong, Wenqi, 2016]{Zhong, Wenqi, 2016, \cite{zhong2016cfd}}
\textit{CFD simulation of dense particulate reaction system: Approaches, recent advances and applications.}

This paper focused on the modeling works in the dense particulate reaction systems. 
Recent advances and applications of the Eulerian-Eulerian approach and the Eulerian-Lagrangian approaches, as well as the limitations.

\section{Modeling}
%
%
%----------------------------------------------------------------//
\subsection[Gidaspow, kinetic theory for bubbling, 1990]{Gidaspow, kinetic theory for bubbling, 1990, \cite{Ding1990}}
\textit{A bubbling fluidization model using kinetic theory of granular flow.}

This is the first time to use the kinetic theory of granular flow to simulate the fluidized bed. 
In this paper, a two dimensional bubbling bed was investigated. 

%
%
%----------------------------------------------------------------//
\subsection[Gidaspow, kinetic theory for riser, 2003]{Gidaspow, kinetic theory for riser, 2003, \cite{Huilin2003}}
\textit{Hydrodynamic simulation of gas-solid flow in a riser using kinetic theory of granular flow.}

\section{Grid Study}
%
%
%----------------------------------------------------------------//
\subsection[Grid study, 2014]{Grid study, \cite{Li2014}}
\textit{Reprint of ``CFD simulations of circulating fluidized bed risers, part I: Grid study''.}

%
%
%----------------------------------------------------------------//
\subsection[Inlet profile study, 2010]{Inlet profile study, \cite{Peng2010}}
\textit{Numerical Study on the Effect of the Air Jets at the Inlet Distributor in the Gas-Solids Circulating Fluidized-Bed Risers.}

%
%
%----------------------------------------------------------------//
\subsection[Grid study, 2005]{Grid study, \cite{AndrewsIV2005}}
\textit{Coarse-grid simulation of gas-particle flows in vertical risers.}

%
%
%----------------------------------------------------------------//
\subsection[Grid study, 2001]{Grid study, \cite{Agrawal2001}}
\textit{The role of meso-scale structures in rapid gas–solid flows.}

%
%
%----------------------------------------------------------------//
\subsection[Grid study, 2001]{Grid study, \cite{Zhang2001}}
\textit{High-resolution three-dimensional numerical simulation of a circulating fluidized bed.}



\section{Ozone Decomposition}
%
%
%----------------------------------------------------------------//
\subsection[2003]{\cite{Therdthianwong2003}}
\textit{Modeling and simulation of circulating fluidized bed reactor with catalytic ozone decomposition reaction.}

%
%
%----------------------------------------------------------------//
\subsection[2004]{\cite{Hansen2004}}
\textit{A three-dimensional simulation of gas/particle flow and ozone decomposition in the riser of a circulating fluidized bed.}

%
%
%----------------------------------------------------------------//
\subsection[2008]{\cite{Dong2008}}
\textit{A multiscale mass transfer model for gas-solid riser flows: Part II-Sub-grid simulation of ozone decomposition.} 



