\chapter{Books}
\section{Modeling}
%
%
%----------------------------------------------------------------//
\subsection[Computational methods for multiphase flow]{Computational methods for multiphase flow, \cite{prosperetti2009computational}}
\textit{Computational methods for multiphase flow.}

This book needs the graduate-level fluid mechanics and numerical methods knowledge as the background. 
The first part introduced the methods for solving the N-S equations by finite difference and finite element methods, which includes computational approach, grid methods for particles, and finite element methods for particulate flows.
The second part introduced the particles models and two-fluid models, which includes point-particle methods, two-fluid methods, and coupled methods. 
Also, the Lattice Boltzmann model was included. 

\section{Fluid Mechanics}
%
%
%----------------------------------------------------------------//
\subsection[A first course in continuum mechanics]{A first course in continuum mechanics, \cite{gonzalez2008first}}
\textit{A first course in continuum mechanics.}

This book is a background material for mathematics. 
The first part introduces the tensor algebra and calculus in three-dimensional Euclidean space. 
For this, \cite{matthews2012vector} can also support. 
The second part introduces the basic equations refer to the fluid mechanics, which includes mass, motion, momentum, energy, and entropy. The third part is not necessary.

The calculus and differential equations should be considered as the fundamental materials.

After this, \cite{wang2014fluid} and \cite{kundu2012fluid} can also support the knowledge for fluid mechanics.

\section{Manual}
%
%
%----------------------------------------------------------------//
\subsection[ANSYS Fluent UDF Manual]{ANSYS Fluent UDF Manual, \cite{udfmanual}}
\textit{ANSYS Fluent UDF Manual.}

The manual for user-defined functions in the ANSYS Fluent. 
UDF is necessary for modifying the inlet profiles and coupling chemical reactions with the fluid models in the software.
%
%
%----------------------------------------------------------------//
\subsection[ANSYS Fluent Theory Guide]{ANSYS Fluent Theory Guide, \cite{FluentTheoryGuide}}
\textit{ANSYS Fluent Theory Guide.}

This manual talks about the theoretical information about the models used in the ANSYS Fluent.

%
%
%----------------------------------------------------------------//
\subsection[C Primer Plus]{C Primer Plus, \cite{Prata:2013:CPP:2578965}}
\textit{C Primer Plus.}

A complete tutorial on C programming.

