%
%
%
\chapter{Ozone Decomposition Experiments from Li, Wang, and Liu}
\section[Li, Dongbing, 2010]{Thesis, \cite{li2010}}
\textit{Investigation of circulating fluidized bed riser and downer reactor performancefor catalytic ozone decomposition.}

Dimension: rise (76 mm i.d., 10.2 m high), downer (76 mm i.d., 5.8 m high). Superficial ags velocity $(U_g)$: $2-5\,\si{m/s}$. 
Solids circulation rate $(G_s)$: $50-100\,\si{kg/(m^2\,s)}$.

In this thesis, the hydrodynamics, ozone decomposition in the riser and downer were studied; 
the performances were compared between riser and downer; 
the ozone distributions in different angular position in riser were studied.

\subsection[Ozone Decomposition In Downer, 2011]{Ozone Decomposition In Downer, \cite{li2011catalytic}}
\textit{Catalytic reaction in a circulating ﬂuidized bed downer: Ozone decomposition.}
\subsubsection{Experimental setup}
\begin{enumerate}
    \item Dimension: rise (76 mm i.d., 10.2 m high), 
    downer (51 mm i.d., 4.9 m high; 76 mm i.d., 5.8 m high), 
    downcomer (203 mm i.d.). 

    \item Superficial gas velocity $(U_g)$: $2,\,3,\,4,\,5\,\si{m/s}$. 
    Solids circulation rate $(G_s)$: $50$ and $100\,\si{kg/(m^2\,s)}$.
    
    \item Air feeding: $T = 22 \cels$, $\mathrm{relative\, humidity} = 19\%$; 
    controlled by a gate valve and measured by a rotameter.
    
    \item Solid feeding: controlled by a ball valve.
    
    \item Gas distribution: aluminum plates ($9.5\,\si{mm}\times 30$ holes and 47$\%$ voids).
    
    \item $\oz / \ox$ feeding: the ozone and oxygen mixture was mixed with air before entering in the downer. The initial ozone concentration ($C_0$) is 10 to 25 ppm.
    
    \item UV ozone analyzer: Model 49i, Thermo Electron Inc.
    
    \item Local solid holdup measurement: PV-5 optical fiber probes.
    
    \item Sampling positions: shown in the Table~\ref{tab:axial sampling positions}.
\end{enumerate}


\begin{table}[h]
    \centering
    \caption{Sampling positions}
    \label{tab:axial sampling positions}
    \begin{tabular}{lccccccccc}
        \toprule
        Axial ($x$) & 0.22 & 0.61 & 1.12 & 1.63 & 2.13 & 2.64 & 3.26 & 4.02 & 4.99 \\
        Radial ($r/R$) & 0 & 0.316 & 0.548 & 0.707 & 0.837 & 0.949 & & &  \\
        \bottomrule
    \end{tabular}
\end{table}


%
%
%----------------------------------------------------------------//
\section[Wang, Chengxiu, 2013]{Wang, Chengxiu, 2013, \cite{wangcx2013}}
\textit{High density gas-solids circulating fluidized bed riser and downer reactors.}

Dimension is the same as the Li, Dongbing's: rise (76 mm i.d., 10.2 m high), downer (76 mm i.d., 5.8 m high). 
Superficial ags velocity $(U_g)$: $3-9\,\si{m/s}$. 
Solids circulation rate $(G_s)$: $100-1000\,\si{kg/(m^2\,s)}$. 
The holdup was much larger than Li's.

Similarly, in this thesis, the hydrodynamics and ozone decomposition in the riser and downer were studied;
the performances were compared between riser and downer; 
the ozone distributions in different angular position in riser were studied.

%
%
%----------------------------------------------------------------//
\section[Liu, Jiangshan, 2016]{Liu, Jiangshan, 2016, \cite{liujs2016}}
\textit{Reactor Performances and Hydrodynamics of Various Gas-Solids Fluidized Beds.}