\chapter{Thesises}
\section{Experiments}
%
%
%----------------------------------------------------------------//
\subsection[Li, Dongbing, 2010]{Li, Dongbing, 2010, \cite{li2010}}
\textit{Investigation of circulating fluidized bed riser and downer reactor performancefor catalytic ozone decomposition.}

Dimension: rise (76 mm i.d., 10.2 m high), downer (76 mm i.d., 5.8 m high). Superficial ags velocity $(U_g)$: $2-5\,\si{m/s}$. 
Solids circulation rate $(G_s)$: $50-100\,\si{kg/(m^2\,s)}$.

In this thesis, the hydrodynamics, ozone decomposition in the riser and downer were studied; 
the performances were compared between riser and downer; 
the ozone distributions in different angular position in riser were studied.

%
%
%----------------------------------------------------------------//
\subsection[Wang, Chengxiu, 2013]{Wang, Chengxiu, 2013, \cite{wangcx2013}}
\textit{High density gas-solids circulating fluidized bed riser and downer reactors.}

Dimension is the same as the Li, Dongbing's: rise (76 mm i.d., 10.2 m high), downer (76 mm i.d., 5.8 m high). 
Superficial ags velocity $(U_g)$: $3-9\,\si{m/s}$. 
Solids circulation rate $(G_s)$: $100-1000\,\si{kg/(m^2\,s)}$. 
The holdup was much larger than Li's.

Similarly, in this thesis, the hydrodynamics and ozone decomposition in the riser and downer were studied;
the performances were compared between riser and downer; 
the ozone distributions in different angular position in riser were studied.

\section{Simulations}
%
%
%----------------------------------------------------------------//
\subsection[Kong, Lei, 2012]{Kong, Lei, 2012, \cite{konglei2012}}
\textit{Numerical simulation of catalytic ozone decomposition reaction in a gas-solids circulating fluidized bed riser.}

Based on the Li's experiments, the numerical simulations were studied in this thesis. 
The two-fluid model (granular kinetic theory) was adopted in the research. 
The effect of the wall boundary conditions were studies. 
The radial and axial profiles of the ozone composition were simulated and compared with the experimental results in Li's.

%
%
%----------------------------------------------------------------//
\subsection[Liu, Yunfeng, 2018]{Liu, Yunfeng, 2018, \cite{liuyf2018}}
\textit{Numerical simulation of three-phase flows in the inverse fluidized bed.}

